% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.90}
\usepackage[urlcolor = black]{hyperref}
\hypersetup{colorlinks=true}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}


\usepackage[noadjust]{cite}
%\usepackage[square,sort,comma,numbers]{natbib}
%\setlength{\bibsep}{0pt}

\bibliographystyle{ieeetr}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Constantinos Chamzas}    & \url{https://cchamzas.com} \\
    Houston, USA                            & chamzas-at-rice.edu   \\
	
\end{tabular*}
\\

\vspace{0.1in}
\resheading{Education}
\begin{itemize}
    \item
    \ressubheading{William Marsh Rice University }{Houston, TX, USA}
	{Ph.D. in Computer Science,
		 Advisor: Dr. Lydia E. Kavraki}{Aug. 2017 -- Present}
	\begin{itemize}
		%\resitem{10 semesters completed}
		\resitem{Research Areas: Integrating Learning and Planning, Planning under Uncertainty, Motion Planning, Task and Motion Planning, Visual Task Planning, Human-Robot interaction}
	\end{itemize}

	
	\item
        \ressubheading{Aristotle University of Thessaloniki }{Thessaloniki, Greece}{Diploma in Electrical and Computer Engineering }{Sep.2011 -- Apr.2017}
	\begin{itemize}
		\resitem{Graduated with 'Excellent', \textbf{8.86/10} cumulative average (Top 2\%)}
		\resitem{Thesis: Structural Analysis of Handwritten Equations Using Probabilistic Context-Free Grammars}
	\end{itemize}
	
		
\end{itemize}
\resheading{Research Experience}

\begin{itemize}
	
    \item
        \ressubheading{Kavraki Lab, \url{http://kavrakilab.org/}}
	{Rice University, Houston}{Graduate Student}
	{Aug. 2017 -- Present  }
	\begin{itemize}
		\resitem{Authored research papers in Robotic Learning}
		\resitem{Developed open-source software for education and research purposes}
	\end{itemize}
\item
\ressubheading{NVIDIA Seattle Robotics Lab, \url{https://nvidia_srl.gitlab.io/}}
{NVIDIA, Seattle}{Research Intern}
{Sept. 2022 -- Dec. 2022}
   \begin{itemize}
   \resitem{Worked on robust Task and Motion Planning}
   \end{itemize}
\item
\ressubheading{Adacomp Lab, \url{https://adacomp.comp.nus.edu.sg/}}
{NUS, Singapore}{Research Intern}
{Jul. 2022 -- Aug. 2022}
    \begin{itemize}
	\resitem{Developed a POMDP formulation for planning with manipulators} 
    \end{itemize}
\item
    \ressubheading{TracLabs Robotics Group, \url{https://traclabs.com/}}
    {TracLabs, Houston}{Research Intern}
    {Jul. 2019 -- Aug. 2019}
    \begin{itemize}
    	\resitem{Integrated a Motion Planning framework and experience-based planning in an industrial problem}
    \end{itemize}
\item
     \ressubheading{Pandora Robotics Group, \url{http://pandora.ee.auth.gr/}}
	{Aristotle University, Thessaloníki}{Software Engineer and Tester}
	{Sep. 2013 -- Feb. 2015}
	\begin{itemize}
		\resitem{Worked or robot mapping and online diagnostic testers} 
	\end{itemize}
\end{itemize}
\resheading{Awards, Nominations and Fellowships}
\begin{itemize}
	\item
	\ressubheading{Future Faculty Fellowship from Rice University}
	{Rice University, Houston}{Awarded to  Ph.D./Postoctoral students applying to tenure-track positions }
	{Sept. 2022}
	\item
	\ressubheading{ICRA 2021 Best Paper nomination in Cognitive Robotics (Top-4)}
	{Rice University, Houston}{Nominated to relevant papers in a competitive basis}
	{Jun. 2021}
	\item
	\ressubheading{NSF Graduate Research Fellowship}
	{Rice University, Houston}{Awarded to outstanding graduate students in the US in STEM }{May. 2019}
	\item
	\ressubheading{ICRA 2019 Travel Grant}
	{Rice University, Houston}{Awarded to attendees in a competitive basis}{Mar. 2019}
	\item
	\ressubheading{Hellenic Professional Society of Texas Scholarship}
	{Rice University, Houston}{Awarded to students with Greek Origins for Academic Excellence}
	{Jan. 2018}
\end{itemize}

\pagebreak

\resheading{Open Source Software}
\begin{itemize}
	\item \ressubheading{MotionBenchMaker}
	{\url{https://github.com/KavrakiLab/motion_bench_maker}}{Core Developer/Maintainer}{January 2022 -- present}
	\item \ressubheading{Pyre Library}
	{\url{https://github.com/KavrakiLab/pyre}}{Core Developer/Maintainer}{April 2021 -- present}
	\item \ressubheading{Robowflex Library}
	{\url{https://github.com/KavrakiLab/robowflex}}{Core Contributor}{March 2019 -- present}
	\item \ressubheading{The Open Motion Planning Library (OMPL)}
	{\url{http://ompl.kavrakilab.org/}}{Contributor}{Jul. 2019 -- present}
\end{itemize}	

\resheading{Teaching Experience}
\begin{itemize}
  	\item
    \ressubheading{Algorithmic Robotics (COMP  450/550) }
    {Rice University, Houston}{Guest Lecturer}
    {Nov. 2022}
    \item
	\ressubheading{Graduate Seminar (COMP  600) }
	{Rice University, Houston}{Instructor Assistant}
	{Sept 2022}
	\item
	\ressubheading{Algorithmic Robotics (COMP  450/550) }
    {Rice University, Houston}{Guest Lecturer}
	{Nov. 2021}
	\item
	\ressubheading{Artificial Intelligence (COMP  440/557) }
	{Rice University, Houston}{Teaching Assistant}
	{Aug. 2019 -- Dec. 2019}
	\item
	\ressubheading{Probabilistic Algorithms and Data Structures (COMP  480/580)}
	{Rice University, Houston}{Teaching Assistant}
	{Jan. 2019 -- May 2019}
	\item
	\ressubheading{Algorithmic Robotics (COMP  450/550) }
	{Rice University, Houston}{Teaching Assistant}
	{Aug. 2018 -- Dec. 2018}
	\item
	\ressubheading{Rice DataScience Bootcamp}
	{Rice University, Houston}{Teaching Assistant}
	{Aug. 2018}
	\item
	\ressubheading{Statistical Machine Learning (COMP 440/540)}
	{Rice University, Houston}{Teaching Assistant}
	{Jan. 2018 -- May. 2018}
\end{itemize}


\resheading{Service}
\begin{description}
	\item[Reviewer:] \textit{IROS}, \textit{ICRA}, \textit{RAL}, \textit{TMECH}, \textit{TRO}
	\item[Invited Talks:] TU Berlin, \textit{IEEE} RAS School, \textit{ICRA} 2023 Workshop 
	\item[Organized Workshops:] ``Evaluating Motion Planning Performance '', \textit{IROS} 2022
\end{description}

\resheading{Skills/Other}
\begin{description}
    \item[Software:] ROS, Keras, Tensorflow, OMPL, MoveIt 
    \item[Programming:] C/C++(Expert), Python(Expert), Java(Intermediate), MATLAB(Intermediate) 
    \item[Languages:] Greek(Mother Tonque), English(Excellent), German(Good) 
    \item[Social:] Officer of Rice University's CS-GSA, Graduate Wellbeing Peer
\end{description}
\resheading{Publications }
\begingroup
	\renewcommand{\section}[2]{}%
\begin{thebibliography}{14}
	   \bibitem{Chamzas2022c}
	\underline{C. Chamzas*}, M. Lippi*, M. C. Welle*, A. Varava, L. E. Kavraki, D. Kragic 
	``Comparing Reconstruction-and Contrastive-based Models for Visual Task Planning'',
	\textit{IEEE/RSJ International Conference on Intelligent Robots and Systems, 2022 (IROS)}, 2022.
	\bibitem{Lee2022}
	 Y. Lee, \underline{C. Chamzas}, and L. E. Kavraki 
	``Adaptive Experience Sampling for Motion Planning using the Generator-Critic Framework'',
	\textit{IEEE Robotics and Automation Letters (RAL), 2022.}
     \bibitem{Chamzas2022c}
     \underline{C. Chamzas*}, F. Eweje* , L. E. Kavraki, E. L. Chaikof 
	``Human Helath and Equity in an Age of Robotics and Intelligent Machines'',
    \textit{National Academy of Medicine Perspectives}, 2022.

    \bibitem{Chamzas2022b}
     \underline{C. Chamzas}, A. Cullen , A. Shrivastava, L. E. Kavraki
	``Learning to Retrieve Relevant Experience for Motion Planning'',
    \textit{IEEE International Conference on Robotics and Automation (ICRA)}, 2022.

    \bibitem{Pena2022}
     C.Quintero-Peña*, \underline{C. Chamzas*}, Z. Sun, V. Unhelkar, L. E. Kavraki
	``Human-Guided Motion Planning in Partially Observable Environments'',
    \textit{IEEE International Conference on Robotics and Automation (ICRA)}, 2022.

    \bibitem{Chamzas2022a}
     \underline{C. Chamzas}, C. Quintero-Peña, Z. Kingston, A. Orthey, D. Rakita, M. Gleicher, M. Toussaint, L. E. Kavraki      ``MotionBenchMaker: A tool to Generate and Benchamark Motion Planning Datasets'',
     \textit{IEEE Robotics and Automation Letters (RAL)}, 2022.  

    \bibitem{Moll2021}
     M. Moll, \underline{C. Chamzas}, Z. Kingston , L. E. Kavraki
     ``HyperPlan: A Framework for Motion Planning Algorithm Selection and Parameter Optimization'',
     \textit{In IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2021.  

    \bibitem{Kingston2021}
     Z.Kingston, \underline{C. Chamzas}, L. E. Kavraki
     ``Using Experience to Improve Constrainted Planning on Foliations for Multi-Modal Problems'',
     \textit{In IEEE/RSJ International Conference on Intelligent Robots and Systems(IROS)}, 2021.  

    \bibitem{Chamzas2020}
    \underline{C. Chamzas}, Z. Kingston, C.Quintero-Peña, A. Shrivastava, L. E. Kavraki
	``Learning sampling distributions using local 3D workspace decompositions for motion planning in high dimensions'',
    \textit{IEEE International Conference on Robotics and Automation (ICRA)}, 2021.
    \textbf{Top-4 finalist for best paper in Cognitive Robotics} 

    \bibitem{Quintero2021}
     C. Quintero-Peña*, \underline{C. Chamzas*}, V.Unhelkar, L.E.Kavraki
	``Motion Planning via Bayesian Learning in the Dark'',
    \textit{In ICRA2021: Workshop on Machine Learning for Motion Planning}, 2021.  

    \bibitem{Pairet2021}
	E. Pairet, \underline{C. Chamzas}, Y. Petillot, L. E. Kavraki
	``Path Planning for Manipulation using Experience-driven Random Trees'',
    \textit{IEEE Robotics and Automation Letters (RAL)}, 2021.
	
  	\bibitem{DChamzas2021} 	
	D. Chamzas, \underline{C. Chamzas}, K. Moustakas
	``cMinMax: A Fast Algorithm to Find the Corners in an N-dimensional Convex Polytope'',
    \textit{International Conference on Computer Graphics Theory and Applications (GRAPP)}, 2021. 

    \bibitem{Chamzas2021} 
	\underline{C. Chamzas*}, M. Lippi* , M. C. Welle*, A.Varava, A.Marino, D. Kragic, L.E.Kavraki
    ``Structuring Latent Representation with Minimal Supervision for Robotic Tasks '',
    \textit{3rd Robot Learning Workshop in NeurIPS}, 2020. 

    \bibitem{Chamzas2019}
	\underline{C. Chamzas}, A. Shrivastava, L. E. Kavraki
	``Using Local Experiences for Global Motion Planning'',
    \textit{IEEE International Conference on Robotics and Automation (ICRA)}, 2019.
   
	\end{thebibliography}
	\endgroup


\end{document}

%\resheading{Other Skills/Interests}
%\begin{description}
%	\item[Service:] Officer of the Computer-Science Graduate Student Association  (CS-GSA).
%	\item[Chess Player :] 2 times local champion in my hometown
%	\item[Running:] Finished 3 half-Marathons and 1 Marathon
%	\item[Sailing:] Acquired Sailing diploma in 2012, I have been sailing the Aegean Sea since 12 years old
%	\item[Boy Scout:]Was active member of the Scout Community for more than 10 years
%	\item[Leadership:]Founded an independent student movement inside the university and won the 2014 student Board elections with 40\% of the votes.The  goal was to help organize the students and participate in the decision making of our university in student related matters.
%\end{description}
	

%\resheading{Notable Projects}
%\begin{itemize}
%	\item Parallel implementation of Conway's Game of Life in C++ and CUDA  \href{https://github.com/vasilish/game_of_life/graphs/contributors}{github\_repo} 
%	\item Parallel implementation of pagerank in C and pthreads \href{https://github.com/orestisf1993/pthread-pagerank/graphs/contributors}{github\_repo}
%	\item My Thesis : Recognition of on-line handwritten mathematical expressions using geometric probabilistic context-free grammars.
%\end{itemize}
%\pagebreak
%\resheading{Sofware Skills}
%\begin{description}
%	\item[Programming Languages:] Assembly, C, C++, C\# ,Python,Java,Matlab,\LaTeX,MySql
%	\item[Operating Systems:]Linux,Android,Windows
%	\item[Software Development:] OOP,Event Programming   
%\end{description}
%\begin{itemize}
	%\item The Open Motion Planning Library  \url{http://ompl.kavrakilab.org/}
%	\item MoveIt Robot Motion Planning Software  \url{https://moveit.ros.org/}
%		\href{https://www.dropbox.com/s/pf5yrej1l3lfokf/Coursera%20interactivepython%202016.pdf?dl=0}{certificate}
%	\item  Game Theory I, II (Stanford University)
%		\href{https://www.dropbox.com/s/utel1aosukvknbk/certificateGameTheory.pdf?dl=0}{certificate}
%	\item  Artificial Intelligence (Berkeley University)
%		\href{https://www.dropbox.com/s/xokddky45ra8s5t/certificateArtificialInteligence.pdf?dl=0}{certificate}
%	\item  Machine Learning (Stanford University)
%		\href{https://www.coursera.org/learn/machine-learning}{course}
%	\item  CNN for Visual Recognition (Stanford University) %\href{http://cs231n.stanford.edu/}{course}
%	\item Modern Robotics (University of Pennsylvania) 
%	%\item Probabilistic Graphical Models (Stanford University) 
%\end{itemize}

%\resheading{Competitions }
%\begin{itemize}
%	\item
%	\ressubheading{IEEEXtreme Programming Competition 9.0,10.0}
%	{Thessaloniki, Greece}
%	{ranked 132/2.447, 126/2.113,
%%	\textit{	,\href{https://www.dropbox.com/s/eszea1e4h4oys0t/certificateXtreeme9.pdf?dl=0}{certificate9}
%%		,\href{https://www.dropbox.com/s/evey861q7mr5q99/IEEEXtreme9Results.pdf?dl=0}{results9}
%%		,\href{https://www.dropbox.com/s/oh0hi22xbxqrq3e/certificateXtreeme10.pdf?dl=0}{certificate10}
%%		,\href{https://www.dropbox.com/s/vtfj1qr54ezt8ac/IEEEXtreme10Results.pdf?dl=0 }{results10}}
%	}
%	{Oct. 2015,Oct. 2016 }
%	\begin{itemize}
%		\resitem{In a 24-hour time span  had  to solve a plethora of programming- algorithmic problems}
%	\end{itemize}
%	\item
%	\ressubheading{CellLock,a cell anti-theft application }{Thessaloniki,Greece}{Team leader,%\href{https://github.com/orestisf1993/daedalus-sfhmmy9/graphs/contributors}{github\_repo}
%		}
%		{March 2016}
%	\begin{itemize}
%		\resitem{During a 2-days workshop developed a thef-protection device for cellphones}
%	\end{itemize}
%	\item
%	\ressubheading{AI block battle competition}{Thessaloniki, Greece}{Ranked 42 /220 in finals. %Currently 50/64, \href{https://github.com/papoudakis/TetrisAiGames/graphs/contributors}{github\_repo}
%		}{April 2016}
%	\begin{itemize}
%		\resitem{Developed a bot playing a 2 player variation of Tetris,
%			%\href{http://theaigames.com/competitions/ai-block-battle/game-log/a/1}{CompetitionPage}(BotName :TetrisMaster)
%			}
%	\end{itemize}
%	
%	
%\end{itemize}

