% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.90}
\usepackage[urlcolor = black]{hyperref}
\hypersetup{colorlinks=true}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}


\usepackage[noadjust]{cite}
%\usepackage[square,sort,comma,numbers]{natbib}
%\setlength{\bibsep}{0pt}

\bibliographystyle{ieeetr}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}
\subsection*{Appendix B}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\Large Constantinos Chamzas}    & \url{https://cchamzas.com} \\
    Worcester, MA, USA                            & cchamzas-at-wpi.edu   \\
	
\end{tabular*}
\\

\vspace{0.1in}
\resheading{Education}
\begin{itemize}
	
    \item
    \ressubheading{William Marsh Rice University }{Houston, TX, USA}
	{Ph.D. in Computer Science, Advisor: Dr. Lydia E. Kavraki}{Aug. 2017 -- May 2023}
	\begin{itemize}
	\resitem{Thesis: Retrieval-Based Learning for Efficient High-DoF Motion Planning}
	\end{itemize}
	\item
    \ressubheading{Aristotle University of Thessaloniki }{Thessaloniki, Greece}{Diploma in Electrical and Computer Engineering }{Sep.2011 -- Apr.2017}
	\begin{itemize}
		\resitem{Graduated with ``Excellent,'' \textbf{8.86/10} cumulative average (Top 2\%)}
		\resitem{Thesis: Structural Analysis of Handwritten Equations Using Probabilistic Context-Free Grammars}
	\end{itemize}
	
		
\end{itemize}
\resheading{Work Experience}

\begin{itemize}
	\item
	\ressubheading{Worcester Polytechnic Institute}{WPI, Worcester}
	{Assistant Professor, Robotics Engineering}{July. 2023 -- Present}
	\begin{itemize}
		\resitem{Research Areas: Learning and Planning, Planning under Uncertainty, Task and Motion Planning}
	\end{itemize}
	
    \item
        \ressubheading{Kavraki Lab, \url{http://kavrakilab.org/}}
	{Rice University, Houston}{Graduate Student}
	{Aug. 2017 -- May 2023  }
	\begin{itemize}
		\resitem{Authored research papers in Robotic Learning}
	\end{itemize}
\item
\ressubheading{NVIDIA Seattle Robotics Lab, \url{https://nvidia_srl.gitlab.io/}}
{NVIDIA, Remote}{Research Intern}
{Sept. 2022 -- Dec. 2022}
   \begin{itemize}
   \resitem{Worked on robust Task and Motion Planning}
   \end{itemize}
\end{itemize}
\resheading{Open Source Software}
\begin{itemize}
	\item \ressubheading{MotionBenchMaker}
	{\url{https://github.com/KavrakiLab/motion_bench_maker}}{Core Developer/Maintainer}{January 2022 -- present}
	\item \ressubheading{Robowflex Library}
	{\url{https://github.com/KavrakiLab/robowflex}}{Core Contributor}{March 2019 -- present}
	\item \ressubheading{The Open Motion Planning Library (OMPL)}
	{\url{http://ompl.kavrakilab.org/}}{Contributor}{Jul. 2019 -- present}
\end{itemize}	

\resheading{Awards, Nominations and Fellowships}
\begin{itemize}
	\item
	\ressubheading{ICRA 2021 Best Paper Top-4 Finalist in Cognitive Robotics}
	{Rice University, Houston}{Nomination of relevant papers in a competitive basis}
	{Jun. 2021}
	\item
	\ressubheading{NSF Graduate Research Fellowship}
	{Rice University, Houston}{Awarded to outstanding graduate students in the US in STEM }{May. 2019}
\end{itemize}

\resheading{Relevant Publications }
\begingroup
\renewcommand{\section}[2]{}%
\begin{thebibliography}{4}
	
	  \bibitem{Chamzas2019}
	\underline{C. Chamzas}, A. Shrivastava, L. E. Kavraki
	``Using Local Experiences for Global Motion Planning'',
	\textit{IEEE International Conference on Robotics and Automation (ICRA)}, 2019.
	
	
		\bibitem{Moll2021}
	M. Moll, \underline{C. Chamzas}, Z. Kingston , L. E. Kavraki
	``HyperPlan: A Framework for Motion Planning Algorithm Selection and Parameter Optimization'',
	\textit{In IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2021.  
	
	 \bibitem{Pairet2021}
	E. Pairet, \underline{C. Chamzas}, Y. Petillot, L. E. Kavraki
	``Path Planning for Manipulation using Experience-driven Random Trees'',
	\textit{IEEE Robotics and Automation Letters (RAL)}, 2021.
	
	
	\bibitem{Chamzas2022a}
	\underline{C. Chamzas}, C. Quintero-Peña, Z. Kingston, A. Orthey, D. Rakita, M. Gleicher, M. Toussaint, L. E. Kavraki      ``MotionBenchMaker: A tool to Generate and Benchamark Motion Planning Datasets'',
	\textit{IEEE Robotics and Automation Letters (RAL)}, 2022.  
	


	
\end{thebibliography}
\endgroup

%\end{itemize}

\end{document}